A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-02-02 supplementary_figures.tex
revision1 done

\renewcommand{\figurename}{Supplementary Figure}

@@

%==================
\begin{document}
\underline{Supplementary information}
% title and author

Supplementary figure legends:

Supplementary figure 1\\
The query results from SurvExpress: Kaplan-Meier plots of 12 genes (the cutoff of high risk and low risk groups, which is derived from risk groups optimization. %cumulative P-value plots).
Inset color scale shows risk groups (high/low) and corresponded RNA expression in high/low.
Thus, the poor prognostic genes are marked as red; the better prognostic genes are marked as orange.

Supplementary figure 2\\
The query results from HPA: Kaplan-Meier plots of  ubiquitin-specific peptidase 10 (USP10) with cutoff by mRNA high expression and low expression groups (P-value = 0.0018).
Over-expression of USP10 has poor prognosis on HNSCC.

Supplementary figure 3\\
GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of high risk and low risk groups, which is derived from cumulative P-value plots). The poor prognostic genes are marked as red; the better prognostic genes are marked as green.

@@

\bibliographystyle{unsrt} %model1-num-names}
\bibliography{TCGA_margin_cutoff.bib}

>>>>

\renewcommand{\figurename}{Supplementary Figure S}

@@

\begin{document}
%%%%%%%%% title
% Full title of the paper (Capitalized)
%\Title{
A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

% MDPI internal command: Title for citation in the left column
%\TitleCitation{A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma}

% Author Orchid ID: enter ID or remove command
%\newcommand{\orcidauthorA}{0000-0002-4476-2600} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0001-6497-4232} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
%\Author{
Li-Hsing Chi $^{1,2}$\orcidA{}, Alexander TH Wu $^{1}$,
Michael Hsiao $^{3}$*
and Yu-Chuan (Jack) Li $^{1,4}$*%\orcidB{}
%\Author{Firstname Lastname $^{1,\dagger,\ddagger}$\orcidA{}, Firstname Lastname $^{1,\ddagger}$ and Firstname Lastname $^{2,}$*}

% MDPI internal command: Authors, for metadata in PDF
%\AuthorNames{Li-Hsing Chi, Alexander TH Wu, Michael Hsiao and Yu-Chuan (Jack) Li}

% MDPI internal command: Authors, for citation in the left column
%\AuthorCitation{Chi, LH.; Wu, ATH.; Hsiao, M.; Li, YCJ.}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
%\address{%

$^{1}$ \quad The Ph.D. Program for Translational Medicine, College of Medical Science and Technology\unskip, 
    Taipei Medical University and Academia Sinica\unskip, Taipei\unskip, Taiwan\\
$^{2}$ \quad Division of Oral and Maxillofacial Surgery, Department of Dentistry\unskip,
    Taipei Medical University Hospital\unskip, Taipei\unskip, Taiwan\\
$^{3}$ \quad Genomics Research Center\unskip, 
    Academia Sinica\unskip, Taipei\unskip, Taiwan\\
$^{4}$ \quad Graduate Institute of Biomedical Informatics, College of Medical Science and Technology\unskip, Taipei Medical University\unskip, Taipei\unskip, Taiwan\\

% Contact information of the corresponding author
%\corres{
Correspondence: Hsiao: mhsiao@gate.sinica.edu.tw; Li: jaak88@gmail.com\\[1cm]
%(optional; include country code; if there are multiple corresponding authors, add author initials) +xx-xxxx-xxx-xxxx (F.L.)}

%==================

%\underline{Supplementary information}
% title and author

\underline{Supplementary figure legends}\\[1cm]

Supplementary Figure S1\\
The query results from SurvExpress: Kaplan-Meier plots of 12 genes (the cutoff of high risk and low risk groups, which is derived from risk groups optimization. %cumulative P-value plots).
Inset color scale shows risk groups (high/low) and corresponded RNA expression in high/low.
Thus, the poor prognostic genes are marked as red; the better prognostic genes are marked as orange.

Supplementary Figure S2\\
The query results from HPA: Kaplan-Meier plots of  ubiquitin-specific peptidase 10 (USP10) with cutoff by mRNA high expression and low expression groups (P-value = 0.0018).
Over-expression of USP10 has poor prognosis on HNSCC.

Supplementary Figure S3\\
GSE2837 query results from PrognoScan: Kaplan-Meier plots of 10 genes (the cutoff of high risk and low risk groups, which is derived from cumulative P-value plots). The poor prognostic genes are marked as red; the better prognostic genes are marked as green.

@@

%\bibliographystyle{unsrt} %model1-num-names}
%\bibliography{TCGA_margin_cutoff.bib}
